Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem

### 2015-07-31 manuscript.tex
adding detail to optimal control formulation. modified gitignore for drive files

\PaperNumber{XX-XXX}

@@

\section{Optimal Control Formulation}\label{sec:optimal_control}
In this section, an optimal control formulation is presented to determine and design transfers within the three body problem.
The concept of reachable sets has seen increased interest by the spacecraft trajectory community.
The reachability set is the set of all positions and velocities that can be achieved over a fixed time space from a defined initial condition, subject to the operational constraints of the spacecraft.
Reachability analysis have been determined using optimal control techniques and level set methods~\cite{mitchell2002}.
They play a critical role in aircraft avoidance and orbital planning.
In this work, an optimal control problem is formulated to generate a reachable set of the spacecraft.
The reachable sets are computed on an appropriate Poincar\`e section and are used to design an appropriate transfer trajectory.

>>>>

\PaperNumber{15-757}

@@

\section{Optimal Control Formulation}\label{sec:optimal_control}
In this section, an optimal control formulation is presented to determine and design transfers within the three body problem.
This formulation is based on the concept of the reachability set on a Poincar\'e section.
This method allows for one to easily determine potential transfer opportunities by finding set intersections on a lower dimensional space and greatly reduces the design process.
The addition of continuous low thrust propulsion extends the control free design process presented in Reference~\citenum{koon2000} and allows for a greater range of potential transfers with a reduced time of flight.

Reachability theory provides a framework to evaluate control capability and safety.  
The reachable set contains all possible trajectories that are achievable over a fixed time horizon from a defined initial condition, subject to the operational constraints of the system.
Reachability theory has been applied to aerospace systems such as collision avoidance, safety planning, and performance characterization.
The theory formally supporting reachability has been extensively developed and is directly derived from optimal control theory~\cite{varaiya2000,lygeros2002,lygeros2004}.
Computation the reachable set for a system involves solving the Hamilton-Jacobi partial differential equation~\cite{mitchell2002}.

Reachability theory has more recently been applied to space systems~\cite{holzinger2009,komendera2012a}.
Computation of reachable sets is critical to space situational awareness and rendezvous and proximity operations.
Maintaining track custody of multiple, potentially maneuvering satellites in close proximity is a challenging problem.
Reachable sets allows for the computation of bounds on the expected region of vehicles.

% more detail on approach
The reachability set is the set of all positions and velocities that can be achieved over a fixed time space from a defined initial condition, subject to the operational constraints of the spacecraft.
Reachability analysis have been determined using optimal control techniques and level set methods~\cite{mitchell2002}.
They play a critical role in aircraft avoidance and orbital planning.
In this work, an optimal control problem is formulated to generate a reachable set of the spacecraft.
The reachable sets are computed on an appropriate Poincar\`e section and are used to design an appropriate transfer trajectory.
